### 2015-04-20 paper.tex
Add caption for cp re dep
Copy/paste introduction from test plan report

\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur
eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui
eu ante cursus gravida non sed sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus,
commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis
maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

\begin{equation}\label{eq:schemeP} 
D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
\end{equation}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cp-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cd-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{cp-re-dep}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{meancontquiv}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{kcont}
\end{figure}

@@

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{bib1}
Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in
South Indian Tamils may be influenced by genetic selection pressure on TLR2 and
TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi:
10.1016/j.molimm.2014.11.005

\bibitem{bib2}
Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a
conceptual framework. Global Health. 2005;1: 14. Available:
http://www.globalizationandhealth.com/content/1/1/14.

\end{thebibliography}

>>>>

\section*{Introduction}
Sandia National Laboratory (SNL) developed the cross-flow turbine, Reference
Model 2 (RM2), to provide an open-source point design for MHK research and
development, including its use as a test object for scaled model testing to
generate power performance data that can be used to validate open-source design
tools. More details on the reference modeling effort are provided in Neary et
al. \cite{Neary2014}.

Dimensional analysis provides scaling laws that are used to upscale model test
data into performance and design information for a full-scale prototype turbine.
For hydrokinetic turbines, hydrodynamic similitude is achieved when the Reynolds
number, Froude number and tip-speed-ratio of the model and the full scale device
match. The Reynolds number is defined as
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq-Re}
\end{equation}
where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
kinematic viscosity. The Froude number is defined as
\begin{equation}
Fr = \frac{U}{\sqrt{gL}},
\label{eq-Fr}
\end{equation}
where $g$ is the gravitational acceleration, and the tip speed ratio is defined
as
\begin{equation}
\lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius.
For hydrokinetic turbine testing, $Re$, not $Fr$, is the dominant scaling
parameter. However, the Froude number (based on blade tip submergence) should
remain small (significantly below one). It is rare to achieve perfect similitude
for $Re$, but a threshold value should be exceeded, such that scale model
results can be extrapolated.

As a cross-flow turbine, the RM2 blades will experience large variations in
angles of attack as they rotate about their axis (``cross-flow turbine'' means
the axis of rotation is perpendicular to flow direction---either vertically or
horizontally). These variations become larger as the tip speed ratio decreases
\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
that the blades operate under dynamic stall, which is a complex unsteady process
and deviates significantly from static foil behavior, during part of the
rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
operate in a higher density fluid, unsteady dynamic effects related to the
blades' pitching motion and flow curvature also become more important when
compared to wind turbines.

The performance of cross-flow MHK turbines thus depends on both Reynolds number
and solidity (note that these issues are related, since an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio, the optimal value for which is a function
of solidity). If numerical models are validated with physical model data that
was obtained at insufficiently high Reynolds numbers, it cannot be determined
whether problems with model predictions are caused by Reynolds number effects,
issues related to higher solidity, or both. It is uncertain whether numerical
models validated with physical model data obtained at low Reynolds number should
be considered validated at all, since the scale at which the model will be
applied is orders of magnitude larger. One way to overcome this uncertainty is
to show that the scaled physical model test has become Reynolds number
independent, and therefore validation efforts should be relevant at full-scale.

For example, the effect of Reynolds number on average power output was shown to
be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
increased with Reynolds number, $Re_c$, along with a shift of the location of
$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
The effects of Reynolds number were quite dramatic over a relatively small range
of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014} showed that turbine performance and near-wake
characteristics become Reynolds number independent at $Re_c \approx 2 \times
10^5$.

The need for experimental data that is relevant to full-scale behavior stems
from the need to validate numerical models---most importantly mid-fidelity
models---desirable for MHK developers to predict the performance of their
cross-flow turbine designs, since physical modeling at appropriate scales can be
prohibitively expensive in the early stages of engineering. Furthermore,
Navier--Stokes-based computational fluid dynamics (CFD) simulations require
modeling in 3 dimensions, which generally necessitates high performance
computing---a resource that is not commonly available, and more expensive.

To date, attempts to validate SNL's mid-fidelity CACTUS vortex line model
\cite{Murray2011} have relied on measurements from the Saint Anthony Falls
Laboratory (SAFL) \cite{Hill2014} and the University of New Hampshire (UNH)
\cite{Neary2013, Michelen2014}. For the SAFL experiments (RM2), the chord
Reynolds number, $Re_c \sim 10^4$, was below the threshold needed to properly
simulate lift and stall characteristics. For the UNH experiment
\cite{Bachant2013}, the chord Reynolds number was sufficiently high at $Re_c
\approx 2.7 \times 10^5$, but the chord/radius ratio and solidity (13.4\%)
created instability in the free-wake evolution in the model, which caused
significant overestimation of power coefficient.

The present task is to acquire a new dataset for the lower solidity RM2 turbine,
but at higher Reynolds numbers than those achieved in the experiments at SAFL.
It is also suspected that the strut drag model in CACTUS could be the source of
some discrepancy. The strut drag will be deliberately modified in the physical
model to provide data to help answer that question. This dataset will be
publicly available for both validation of CACTUS and other numerical models.
This report details the experimental test plan for acquiring, processing, and
archiving this data, which includes development of a scaled physical model, and
descriptions of the experimental setup and procedure to be performed in a towing
tank at the University of New Hampshire (UNH).

\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cp-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cd-curves}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Power Coefficient Reynolds Number Dependence.}
Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{cp-re-dep}
\end{figure}

@@

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{meancontquiv}
\end{figure}

\begin{figure}[h]
%\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{kcont}
\end{figure}

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\bibliography{library}
